Bayesian multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-08-20 manuscript/manuscript.tex
revisions

\subsection{Simulation to Assess Sensitivity to Misspecified K}

Our final simulation is concerned with validating the use of WAIC for determining the number of clusters $K$. To this end, we simulate data from the same MSN mixture as in simulation study \#2, that is --- we simulate data from a $K = 3$ cluster model and fit MSN mixtures of $K \in \{2,3,4\}$, comparing the WAIC under each setting of $K$. Additionally, we investigate to what degree fitting the MVN model to data generated from a MSN model affects the choice of $K$, using WAIC to select the optimal $K$.

>>>>

\subsection{Simulation to Validate Choice of K}

Our final simulation is concerned with validating the use of WAIC for determining the number of clusters, $K$. To this end, we generate data sets from MSN models with $K = \{2,3,4\}$. To each simulated data set, we fit three of our proposed Bayesian MSN models with $K = \{2,3,4\}$ and compute WAIC for each model. As shown in Table 2, we are able to correctly estimate the true value of $K$ using WAIC, as the best fitting model for each simulation setting is the model with lowest WAIC. We note that, for the simulated data with $K = 2$, we were not able to fit a 4-cluster MSN model due to the occurence of vacant clusters during MCMC estimation.

\begin{table}[]
\centering
\begin{tabular}{lllll}
 &  &  & \textbf{Fitted} &  \\
 &  & \textit{K = 2} & \textit{K = 3} & \textit{K = 4} \\ \cline{3-5} 
 & \multicolumn{1}{l|}{\textit{K = 2}} & 11624 \multicolumn{1}{l|}{} & 16988 \multicolumn{1}{l|}{} & * \multicolumn{1}{l|}{} \\ \cline{3-5} 
\textbf{Truth} & \multicolumn{1}{l|}{\textit{K = 3}} & 25681 \multicolumn{1}{l|}{} & 18062 \multicolumn{1}{l|}{} & 23519 \multicolumn{1}{l|}{} \\ \cline{3-5} 
 & \multicolumn{1}{l|}{\textit{K = 4}} & 19305\multicolumn{1}{l|}{} & 21415 \multicolumn{1}{l|}{} & 12232 \multicolumn{1}{l|}{} \\ \cline{3-5} 
\end{tabular}
\end{table}
